Cybercrime and Online Video Games

### 2019-12-14 paper/paper.tex
Update paper.tex

Each algorithm gives each comment a probability to be either positive or negative. 
We sum each algorithm's score and determine based on that score whether the comment is positive, negative or neutral. Below is a chart
showing the percentage of comments that were deemed positive, negative and neutral.

@@

@@

\begin{figure}[h]
\centering
\begin{subfigure}{.25\textwidth}
 	\centering
	\includegraphics[width = .4\linewidth]{ThreadCount.png}
	\caption{Thread Count}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
 	\centering
	\includegraphics[width=.4\linewidth]{CommentCount.png}
	\caption{Comment Count}
\end{subfigure}
\caption{Thread and Comment Pie Charts}
\end{figure}

>>>>

Each algorithm gives each comment a probability to be either positive, negative or neutral. It also classifies whether a comment 
involves a trade or a Q&A with the thread poster. We sum each algorithm's score and determine based on that score whether the comment is 
positive, negative or neutral. Below are charts showing the percentage of comments that were deemed positive, negative and neutral, 
percentage of comments involving a trade and percentage of comments with a Q&A.

@@

Along with the webscraper was some manual analysis. Because we could not find out all information about a thread or comment from the
webscraping, we had to manually enter in some data. One of the categories we had to manually analyze was the payment type for the
product or service the poster was selling. The payments methods ranged from standard credit cards all the way to gift cards. Below is 
a chart depicting the distribution of payment methods. Please keep in mind that not all posters stated the payment methods and some
posts allow for more than one type.

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{PaymentChart.png}
	\caption{Sentiment Analysis Chart}
\end{figure}

@@

\begin{figure}[h]
 	\centering
	\includegraphics[width = .5\linewidth]{ThreadCount.png}
	\caption{Thread Count}
\end{figure}
\begin{figure}[h]
 	\centering
	\includegraphics[width=.5\linewidth]{CommentCount.png}
	\caption{Comment Count}
\end{figure}
